Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
add ref to local picture

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}

@@

\subsection{Learning Schemes}
Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE).

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}
%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cleveref}

@@

\subsection{Learning Schemes}
\begin{figure}
  \centering
  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-ctde.pdf}
  \includegraphics[width=0.49\linewidth]{figures/learning-scheme-dtde.pdf}
  \caption{Graphical rap presentation of centralized training with decentralized execution (left) and decentralized training with decentralized execution (rigth) in multi-agent reinforcement learning.}
  \label{fig:learning_paradigms}
\end{figure}
Multi-agent learning can be categorized based on the training scheme and the information accessibility for agents. 
Two prominent paradigms are centralized training with decentralized execution (CTDE) and decentralized training with decentralized execution (DTDE)---see \Cref{fig:learning_paradigms}.
